Manuscript analyses

### 2024-01-26 cilta_cel/Manuscript analyses.Rmd
Add infection categories, HLH, violin plots replacing cumulative incidence plots, ...

Characteristics <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "CHARACTERISTICS AND OUTCOMES ", skip = 1)
Counts <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "COUNTS")
Infections <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "INFECTIONS")
Support <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "SUPPORT")
Pneumo_titers <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "BACTERIAL AND VIRAL TITERS")
Apheresis <- 
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "APHERESIS")
id_to_modify_neurotox <- 
  read_csv(
    paste0(here(), 
           "/cilta_cel/patient id who had icans and delayed neurotox - need to change neurotox type to PRES.csv"))
```

```{r join}
cart <- full_join(Characteristics, Counts, by = "PT Identifier") %>% 
  full_join(., Infections, by = "PT Identifier") %>% 
  full_join(., Support, by = "PT Identifier") %>% 
  full_join(., Pneumo_titers, by = "PT Identifier") %>% 
  # select(-`Date of leukapheresis.y`, `Date of leukapheresis` = `Date of leukapheresis.x`) %>% 
  full_join(., Apheresis, by = "PT Identifier") %>% 
  janitor::clean_names()
```

@@

```{r data cleaning}
cart <- cart %>% 
  # General ----
  # Fix letter case and missing
  mutate(across(where(is.character), ~ str_replace(., "NE|ND|N/A|Not done", NA_character_))) %>%
  mutate(across(c(where(is.character),
                  -c("pt_identifier",
                     "r_iss_at_car_t_infusion")), 
                ~ str_to_sentence(.) )) %>%
  mutate(across(c(contains("vgpr"), "response_to_bridging_chemotherapy"
                  ), 
                ~ str_to_upper(.) )) %>%

  mutate(across(where(is.character), ~ str_replace(., "Unknown|unknown", NA_character_))) %>%
  # Create site variable
  mutate(site = case_when(
    str_detect(pt_identifier, "MCC")               ~ "Moffitt",
    str_detect(pt_identifier, "CCT")               ~ "Stanford",
    str_detect(pt_identifier, "KUMC")              ~ "KUMC",
    str_detect(pt_identifier, "MDA")               ~ "MD Anderson?",
    str_detect(pt_identifier, "Utah")              ~ "Utah"
  )) %>%
  # Suboptimal is NA
  mutate(across(c(#"bm_plasma_cell_percent_at_pre_ld",
                  "high_marrow_burden_50_percent",
                  # contains("normo_hypo_hyper"),
                  contains("fibrosis"),
                  contains("dysplasia"),
                  "b2_microglobulin_day_180"), 
                ~ str_replace(., "Suboptimal", NA_character_))) %>%
  # Are numerical - also remove "Suboptimal"
  mutate(across(c(starts_with("marrow_fibrosis"),
                  starts_with("ldh_")
                  ), 
                ~ as.numeric(.))) %>%
  mutate(across(c("response_to_bridging_chemotherapy"), 
                ~ str_replace(., "Not evaluable", NA_character_))) %>% 
  # Convert 0/1 to No/Yes
  mutate_at(c("infection_yes_1_no_0",
              "severe_infection_need_for_iv_antibiotics_and_or_hospitalization_yes_1_no_0",
              # "bm_plasma_cell_percent_at_pre_ld",
              # "high_marrow_burden_50_percent",
              # "ECOG > or = 2? (Yes, No)",
              # deletion_17p_prior_to_car_t_infusion_yes_no,
              # "t_4_14_prior_to_car_t_infusion_yes_no",
              # "t_14_16_prior_to_car_t_infusion_yes_no",
              # "steroid_use_yes_no", "tocilizumab_yes_no", "anakinra_yes_no",
              # "Bridging Therapy (Yes=1, No=0)",
              # "Received alkylating therapy with bridging (Yes=1, No=0)",
              "need_for_g_csf_post_infus_yes_1_no_0",
              "need_for_ivig_yes_1_no_0",
              "cd34_stem_cell_boost_yes_1_no_0",
              "rbc_transfusion_within_30d_post_cart_yes_1_no_0", "plt_transfusion_within_30d_post_cart_yes_1_no_0", 
              "rbc_transfusion_30d_post_cart_yes_1_no_0", "plt_transfusion_30d_post_cart_yes_1_no_0",
              "tpo_agonist_post_cart_yes_1_no_0"), 
            ~ case_when(
              . == 1                                              ~ "Yes",
              . == 0                                              ~ "No",
              TRUE                                                ~ NA_character_
            )) %>% 
  # Marrow ----
  mutate(marrow_cellularity_baseline_normo_hypo_hyper = case_when(
    marrow_cellularity_baseline_normo_hypo_hyper == "\"patchy\""                 ~ "hyper",
    TRUE                                                          ~ marrow_cellularity_baseline_normo_hypo_hyper
  )) %>%
  mutate(marrow_cellularity_day_30_normo_hypo_hyper = case_when(
    marrow_cellularity_day_30_normo_hypo_hyper == "aplastic"                    ~ "hypo",
    TRUE                                                          ~ marrow_cellularity_day_30_normo_hypo_hyper
  )) %>%
  # Separate variable cellularity
  mutate(across(c(starts_with("marrow_cellularity_") & ends_with("normo_hypo_hyper")), ~ case_when(
    . == "Variable"                         ~ "Yes"
  ), .names = "is_variable_{.col}")) %>% 
  mutate(across(c(starts_with("marrow_cellularity_") & ends_with("normo_hypo_hyper")), ~ case_when(
    . == "Pauci"                            ~ "Hypo",
    . == "Variable"                         ~ NA_character_,
    TRUE                                    ~ .
  ))) %>%

@@

  mutate(day_of_neutrophil_recovery_ = case_when(

@@

@@

@@

             end = day_of_neutrophil_recovery)/
  ), day_of_neutrophil_recovery = coalesce(day_of_neutrophil_recovery_, day_of_neutrophil_recovery)) %>% 
  select(-day_of_neutrophil_recovery_) %>% 

@@

@@

@@

@@

```{r infection}
cart6 <- cart6 %>%
  # Infection ----
  mutate(any_infection = infection_yes_1_no_0
  ) %>%
  mutate(any_sevinfection = severe_infection_need_for_iv_antibiotics_and_or_hospitalization_yes_1_no_0
  ) %>% 
  mutate(time_from_infusion_to_infection_days = 
           interval(
             start = date_of_car_t_infusion, 
             end = date_of_infection)/
           duration(n=1, units = "days"))

@@

```{r delayed NT}
cilta <- cart6 %>%
  mutate(what_non_parkinsonian_neurotoxicity = case_when(
    what_non_parkinsonian_neurotoxicity == "Delayed icans, hippocampal sclerosis/gliosis"
                                                                  ~ "cerebral edema/PRES",
    TRUE                                                          ~ what_non_parkinsonian_neurotoxicity
  )) %>% 
  mutate(other_delayed_non_parkinsonian_neurologic_toxicity_yes_no = case_when(
    is.na(other_delayed_non_parkinsonian_neurologic_toxicity_yes_no) 
                                                                  ~ "No",
    TRUE           ~ other_delayed_non_parkinsonian_neurologic_toxicity_yes_no
  )) %>%
  mutate(parkinsonian_neurotoxicity_yes_no = case_when(
    str_detect(pt_identifier, id_to_modify_neurotox$id)           ~ "No",
    parkinsonian_neurotoxicity_yes_no == "Yes" & 
      what_non_parkinsonian_neurotoxicity == "Bell's palsy"       ~ "No",
    is.na(parkinsonian_neurotoxicity_yes_no)                      ~ "No",
    TRUE                                                          ~ parkinsonian_neurotoxicity_yes_no
  )) %>%
  mutate(delayed_neuro = case_when(
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" |
      parkinsonian_neurotoxicity_yes_no == "Yes"                  ~ "Yes",
    TRUE                                                          ~ "No"
  )) %>%
  mutate(delayed_neuro_type = case_when(
    str_detect(pt_identifier, id_to_modify_neurotox$id)           ~ "PRES",
    what_non_parkinsonian_neurotoxicity == "cerebral edema/PRES"
                                                                  ~ "PRES",
    what_non_parkinsonian_neurotoxicity == "Aidp"                 ~ "Polyneuropathy",
    what_non_parkinsonian_neurotoxicity == 
      "Posterior reversible encephalopathy syndrome (pres) and parkinsonism" 
                                                                  ~ "Parkinsonian/PRES",
    what_non_parkinsonian_neurotoxicity == 
      "Posterior reversible encephalopathy syndrome (pres); progressive multifocal leukoencephalopathy (pml)" 
                                                                  ~ "PRES/PML",
    parkinsonian_neurotoxicity_yes_no == "Yes"                    ~ "Parkinsonian",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "alsy")     ~ "Bell's palsy",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "alsey")    ~ "Bell's palsy", 
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "droop")    ~ "Bell's palsy", 
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "PRES")    ~ "PRES", 
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "dysautonomia") 
                                                                 ~ "Dysautonomia",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "plopia")    
                                                                  ~ "Diplopia",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "Polyneuropathy") 
                                                                  ~ "Polyneuropathy",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      is.na(what_non_parkinsonian_neurotoxicity)                  ~ "Unknown type",
    TRUE                                                          ~ what_non_parkinsonian_neurotoxicity
  )) 
```

@@

@@

## Table 2. Clinical outcomes
```{r}
tbl1 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select(max_crs_grade_0_5, CRS_gradecat,
         day_of_onset_crs_relative_to_infusion,
         day_of_max_crs_relative_to_infusion,
         duration_of_crs_days, 
         max_icans, ICANS_gradecat,
         day_of_onset_icans_relative_to_infusion,
         day_of_max_icans_relative_to_infusion,
         duration_of_icans_days,
         delayed_neuro,
         parkinsonian_neurotoxicity_yes_no,
         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
         delayed_neuro_type) %>% 
  tbl_summary(type = list(
    c(day_of_onset_crs_relative_to_infusion,
         day_of_max_crs_relative_to_infusion,
         duration_of_crs_days,
      day_of_onset_icans_relative_to_infusion,
         day_of_max_icans_relative_to_infusion,
         duration_of_icans_days) ~ "continuous",
    c(delayed_neuro,
         parkinsonian_neurotoxicity_yes_no,
         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no) 
    ~ "categorical"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max})"),
    digits = all_continuous() ~ 1,
    missing = "no"
    ) %>% 
  bold_labels() %>% add_stat_label()

@@

## Table S8.Details of infections after ide-cel
```{r infection details 30 first days}
tbl1 <- cilta %>% 
  filter(time_from_infusion_to_infection_days <= 30) %>% 
  select(infection_type_bacterial_viral_fungal_parasitic) %>% 
  tbl_summary() %>%
  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
                  type= "level",
                  level_value = c("Fungal", "Viral")) %>%
  remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>%
  add_stat_label(label = infection_type_bacterial_viral_fungal_parasitic ~ c("n (%)"), location = "column") %>%
  modify_column_indent(columns = label, undo = TRUE) %>% 
  bold_levels() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Infections in the first 30 days**")

@@

## Patients with infections by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy
```{r Patients with infections by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy}
cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select(number_prior_lines_therapy,
         number_of_prior_lines_of_therapy,
         prior_auto_sct_yes_no,
         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
         Prior_bcma_therapy,
         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
         # `Days from last bridging to CAR-T infusion`,
         cell_dose_million_cells,
         need_for_g_csf_post_infus_yes_1_no_0,
         cd34_stem_cell_boost_yes_1_no_0,
         need_for_ivig_yes_1_no_0,

         CRS_gradecat, ICANS_gradecat,
         delayed_neuro,
         parkinsonian_neurotoxicity_yes_no,
         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
         delayed_neuro_type,
         steroid_use_yes_no, 
         tocilizumab_yes_no, anakinra_yes_no,
         bridging_therapy_yes_no, any_infection) %>% 
  tbl_summary(by= any_infection, 
              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
              type = list(all_dichotomous() ~ "categorical", 
                          number_of_prior_lines_of_therapy ~ "continuous")) %>%
  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Any infection**")

@@

         CRS_gradecat, ICANS_gradecat,
         delayed_neuro,
         parkinsonian_neurotoxicity_yes_no,
         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
         delayed_neuro_type,
         steroid_use_yes_no, 
         tocilizumab_yes_no, anakinra_yes_no,
         bridging_therapy_yes_no, any_sevinfection) %>% 
  tbl_summary(by=any_sevinfection, 
              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
              type = list(all_dichotomous() ~ "categorical", 
                          number_of_prior_lines_of_therapy ~ "continuous")) %>%
  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Any severe infection**")
```

>>>>

Characteristics <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "CHARACTERISTICS AND OUTCOMES ", skip = 1)
Counts <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "COUNTS")
Infections <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "INFECTIONS")
Support <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "SUPPORT")
Pneumo_titers <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "BACTERIAL AND VIRAL TITERS")
Apheresis <- 
  readxl::read_xlsx(paste0(here(), "/cilta_cel/Carvykti cellularity_11202023.xlsx"),
                    sheet = "APHERESIS")
id_to_modify_neurotox <- 
  read_csv(
    paste0(here(), 
           "/cilta_cel/patient id who had icans and delayed neurotox - need to change neurotox type to PRES.csv"))

infections_cat <- 
  read_csv(
    paste0(here(), 
           "/cilta_cel/Infections categorized.csv")) %>% 
  distinct() %>% 
  purrr::keep(~!all(is.na(.))) %>% 
  rename("infection_type_cat" = `...14`) %>% 
  drop_na(infection_type_details) %>% 
  add_row(infection_type_bacterial_viral_fungal_parasitic = "Bacterial", 
          infection_type_details = "Pna, unknown organism (covid -) resulting in ards and death",
          infection_type_cat = "Respiratory infections")

viral_cat <- 
  read_csv(
    paste0(here(), 
           "/cilta_cel/Infections categorized.csv DKH.csv")) %>% 
  distinct() %>% 
  janitor::clean_names() %>% 
  select(-c(x4,x5))

HLH <-
  readxl::read_xlsx(paste0(here(), "/cilta_cel/HLH.xlsx"))
```

```{r join}
cart <- full_join(Characteristics, Counts, by = "PT Identifier") %>% 
  full_join(., Infections, by = "PT Identifier") %>% 
  full_join(., Support, by = "PT Identifier") %>% 
  full_join(., Pneumo_titers, by = "PT Identifier") %>% 
  # select(-`Date of leukapheresis.y`, `Date of leukapheresis` = `Date of leukapheresis.x`) %>% 
  full_join(., Apheresis, by = "PT Identifier") %>% 
  left_join(., HLH, by = c("PT Identifier" = "PT Identifier (DO NOT USE PHI)")) %>% 
  janitor::clean_names()
```

@@

```{r data cleaning}
cart <- cart %>% 
  # General ----
  # Fix letter case and missing
  mutate(across(where(is.character), ~ str_replace(., "NE|ND|N/A|Not done", NA_character_))) %>%
  mutate(across(c(where(is.character),
                  -c("pt_identifier",
                     "r_iss_at_car_t_infusion")), 
                ~ str_to_sentence(.) )) %>% 
  # Merge with infection and viral group here afetr str_to_sentence
  left_join(., infections_cat,
            by = c("infection_type_bacterial_viral_fungal_parasitic", "infection_type_details")) %>%
  left_join(., viral_cat,
            by = c("infection_type_bacterial_viral_fungal_parasitic", "infection_type_details")) %>%
  mutate(across(c(contains("vgpr"), "response_to_bridging_chemotherapy"
                  ), 
                ~ str_to_upper(.) )) %>%

  mutate(across(where(is.character), 
                ~ str_replace(., "^Unknown$|^unknown$|^UNKNOWN$", NA_character_))) %>%
  # Create site variable
  mutate(site = case_when(
    str_detect(pt_identifier, "MCC")               ~ "Moffitt",
    str_detect(pt_identifier, "CCT")               ~ "Stanford",
    str_detect(pt_identifier, "KUMC")              ~ "KUMC",
    str_detect(pt_identifier, "MDA")               ~ "MD Anderson?",
    str_detect(pt_identifier, "Utah")              ~ "Utah"
  )) %>%
  # Suboptimal is NA
  mutate(across(c(#"bm_plasma_cell_percent_at_pre_ld",
                  "high_marrow_burden_50_percent",
                  # contains("normo_hypo_hyper"),
                  contains("fibrosis"),
                  contains("dysplasia"),
                  "b2_microglobulin_day_180"), 
                ~ str_replace(., "Suboptimal", NA_character_))) %>%
  # Are numerical - also remove "Suboptimal"
  mutate(across(c(starts_with("marrow_fibrosis"),
                  starts_with("ldh_")
                  ), 
                ~ as.numeric(.))) %>%
  mutate(across(c("response_to_bridging_chemotherapy"), 
                ~ str_replace(., "Not evaluable", NA_character_))) %>% 
  # Convert 0/1 to No/Yes
  mutate_at(c("infection_yes_1_no_0",
              "severe_infection_need_for_iv_antibiotics_and_or_hospitalization_yes_1_no_0",
              # "bm_plasma_cell_percent_at_pre_ld",
              # "high_marrow_burden_50_percent",
              # "ECOG > or = 2? (Yes, No)",
              # deletion_17p_prior_to_car_t_infusion_yes_no,
              # "t_4_14_prior_to_car_t_infusion_yes_no",
              # "t_14_16_prior_to_car_t_infusion_yes_no",
              # "steroid_use_yes_no", "tocilizumab_yes_no", "anakinra_yes_no",
              # "Bridging Therapy (Yes=1, No=0)",
              # "Received alkylating therapy with bridging (Yes=1, No=0)",
              "need_for_g_csf_post_infus_yes_1_no_0",
              "need_for_ivig_yes_1_no_0",
              "cd34_stem_cell_boost_yes_1_no_0",
              "rbc_transfusion_within_30d_post_cart_yes_1_no_0", "plt_transfusion_within_30d_post_cart_yes_1_no_0", 
              "rbc_transfusion_30d_post_cart_yes_1_no_0", "plt_transfusion_30d_post_cart_yes_1_no_0",
              "tpo_agonist_post_cart_yes_1_no_0"), 
            ~ case_when(
              . == 1                                              ~ "Yes",
              . == 0                                              ~ "No",
              TRUE                                                ~ NA_character_
            )) %>% 
  # Marrow ----
  mutate(marrow_cellularity_baseline_normo_hypo_hyper = case_when(
    marrow_cellularity_baseline_normo_hypo_hyper == "\"patchy\""                 ~ "hyper",
    TRUE                                                          ~ marrow_cellularity_baseline_normo_hypo_hyper
  )) %>%
  mutate(marrow_cellularity_day_30_normo_hypo_hyper = case_when(
    marrow_cellularity_day_30_normo_hypo_hyper == "aplastic"                    ~ "hypo",
    TRUE                                                          ~ marrow_cellularity_day_30_normo_hypo_hyper
  )) %>%
  # Separate variable cellularity
  mutate(across(c(starts_with("marrow_cellularity_") & ends_with("normo_hypo_hyper")), ~ case_when(
    . == "Variable"                         ~ "Yes"
  ), .names = "is_variable_{.col}")) %>% 
  mutate(across(c(starts_with("marrow_cellularity_") & ends_with("normo_hypo_hyper")), ~ case_when(
    . == "Pauci"                            ~ "Hypo",
    . == "Variable"                         ~ NA_character_,
    TRUE                                    ~ .
  ))) %>%

@@

  mutate(day_of_neutrophil_recovery_KUMC = case_when(

@@

  mutate(ivig_last_date_beyond_pd = case_when(
    last_date_of_ivig == "Beyond pd"       ~ "Yes"

@@

  mutate(date_of_neutrophil_recovery = day_of_neutrophil_recovery,
         date_of_neutrophil_recovery = case_when(
           date_of_neutrophil_recovery < date_of_car_t_infusion    ~ NA_Date_,
           TRUE                                                    ~ date_of_neutrophil_recovery
             end = date_of_neutrophil_recovery)/
  ), day_of_neutrophil_recovery = coalesce(day_of_neutrophil_recovery_KUMC, day_of_neutrophil_recovery)) %>% 

@@

@@

  ), first_day_of_ivig = case_when(
    first_day_of_ivig >= 0                                         ~ first_day_of_ivig,
    TRUE                                                           ~ NA_real_
  mutate(last_date_of_ivig = case_when(
    ivig_last_date_beyond_pd == "Yes"                              ~ as.Date(as.numeric(date_of_pd),origin = "1899-12-30"),
    TRUE                                                           ~ last_date_of_ivig

@@

  ), last_day_of_ivig = case_when(
    last_day_of_ivig >= 0                                          ~ last_day_of_ivig,
    TRUE                                                           ~ NA_real_
  mutate(need_for_ivig_yes_1_no_0 = case_when(
    first_date_of_ivig < date_of_car_t_infusion |
      last_date_of_ivig < date_of_car_t_infusion                   ~ "No",
    TRUE                                                           ~ need_for_ivig_yes_1_no_0

@@

    date_of_neutrophil_recovery < date_of_car_t_infusion        ~ "No",

@@

```{r infection}
cart6 <- cart6 %>%
  # Infection ----
  mutate(time_from_infusion_to_infection_days = 
           interval(
             start = date_of_car_t_infusion, 
             end = date_of_infection)/
           duration(n=1, units = "days"), 
         time_from_infusion_to_infection_days = case_when(
    time_from_infusion_to_infection_days >= 0     ~ time_from_infusion_to_infection_days,
    TRUE                                          ~ NA_real_
    )) %>% 
  mutate(any_infection = case_when(
    time_from_infusion_to_infection_days >= 0     ~ infection_yes_1_no_0,
    TRUE                                          ~ "No"
  )) %>%
  mutate(any_sevinfection = case_when(
    time_from_infusion_to_infection_days >= 0     ~ severe_infection_need_for_iv_antibiotics_and_or_hospitalization_yes_1_no_0,
    TRUE                                          ~ "No"
  )) %>% 
  mutate(across(c("infection_type_details", "infection_type_bacterial_viral_fungal_parasitic",
                  "infection_type_cat"), ~ case_when(
    time_from_infusion_to_infection_days >= 0     ~ .,
    TRUE                                          ~ NA_character_
  )))

@@

```{r delayed NT}
cilta <- cart6 %>%
  mutate(what_non_parkinsonian_neurotoxicity = case_when(
    what_non_parkinsonian_neurotoxicity == "Delayed icans, hippocampal sclerosis/gliosis"
                                                                  ~ "cerebral edema/PRES",
    TRUE                                                          ~ what_non_parkinsonian_neurotoxicity
  )) %>% 
  mutate(other_delayed_non_parkinsonian_neurologic_toxicity_yes_no = case_when(
    is.na(other_delayed_non_parkinsonian_neurologic_toxicity_yes_no) 
                                                                  ~ "No",
    TRUE           ~ other_delayed_non_parkinsonian_neurologic_toxicity_yes_no
  )) %>%
  mutate(parkinsonian_neurotoxicity_yes_no = case_when(
    str_detect(pt_identifier, id_to_modify_neurotox$id)           ~ "No",
    parkinsonian_neurotoxicity_yes_no == "Yes" & 
      what_non_parkinsonian_neurotoxicity == "Bell's palsy"       ~ "No",
    is.na(parkinsonian_neurotoxicity_yes_no)                      ~ "No",
    TRUE                                                          ~ parkinsonian_neurotoxicity_yes_no
  )) %>%
  mutate(delayed_neuro = case_when(
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" |
      parkinsonian_neurotoxicity_yes_no == "Yes"                  ~ "Yes",
    TRUE                                                          ~ "No"
  )) %>%
  mutate(delayed_neuro_type = case_when(
    str_detect(pt_identifier, id_to_modify_neurotox$id)           ~ "PRES",
    what_non_parkinsonian_neurotoxicity == "cerebral edema/PRES"
                                                                  ~ "PRES",
    what_non_parkinsonian_neurotoxicity == "Aidp" |
      what_non_parkinsonian_neurotoxicity == "Slowed cognition"   ~ "Polyneuropathy",
    what_non_parkinsonian_neurotoxicity == 
      "Posterior reversible encephalopathy syndrome (pres) and parkinsonism" 
                                                                  ~ "Parkinsonian/PRES",
    what_non_parkinsonian_neurotoxicity == 
      "Posterior reversible encephalopathy syndrome (pres); progressive multifocal leukoencephalopathy (pml)" 
                                                                  ~ "PRES/PML",
    parkinsonian_neurotoxicity_yes_no == "Yes"                    ~ "Parkinsonian",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "alsy")     ~ "Bell's palsy",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "alsey")    ~ "Bell's palsy", 
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "droop")    ~ "Bell's palsy", 
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "PRES")    ~ "PRES", 
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "dysautonomia") 
                                                                 ~ "Dysautonomia",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "plopia")    
                                                                  ~ "Diplopia",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      str_detect(what_non_parkinsonian_neurotoxicity, "Polyneuropathy") 
                                                                  ~ "Polyneuropathy",
    other_delayed_non_parkinsonian_neurologic_toxicity_yes_no == "Yes" &
      is.na(what_non_parkinsonian_neurotoxicity)                  ~ "Unknown type",
    TRUE                                                          ~ what_non_parkinsonian_neurotoxicity
  )) 
```

@@

                         hlh = "HLH", hlh_hlh_like_toxicities = "HLH/HLH-Like Toxicities?",

@@

## Table 2. Clinical outcomes
```{r}
tbl1 <- cilta %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select(max_crs_grade_0_5, CRS_gradecat,
         day_of_onset_crs_relative_to_infusion,
         day_of_max_crs_relative_to_infusion,
         duration_of_crs_days, 
         max_icans, ICANS_gradecat,
         day_of_onset_icans_relative_to_infusion,
         day_of_max_icans_relative_to_infusion,
         duration_of_icans_days,
         delayed_neuro,
         parkinsonian_neurotoxicity_yes_no,
         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
         delayed_neuro_type,
         hlh, hlh_hlh_like_toxicities) %>% 
  tbl_summary(type = list(
    c(day_of_onset_crs_relative_to_infusion,
         day_of_max_crs_relative_to_infusion,
         duration_of_crs_days,
      day_of_onset_icans_relative_to_infusion,
         day_of_max_icans_relative_to_infusion,
         duration_of_icans_days) ~ "continuous",
    c(delayed_neuro,
         parkinsonian_neurotoxicity_yes_no,
         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no) 
    ~ "categorical"),
    statistic=list(all_continuous() ~ "{median} ({min}, {max})"),
    digits = all_continuous() ~ 1,
    missing = "no"
    ) %>% 
  bold_labels() %>% add_stat_label()

@@

## Table S8. Details of infections after ide-cel
Patients can be counted multiple times if multiple infections.
```{r infection details 30 first days}
tbl1 <- cilta %>% 
  filter(time_from_infusion_to_infection_days <= 30) %>% 
  select(infection_type_bacterial_viral_fungal_parasitic) %>% 
  tbl_summary() %>%
  remove_row_type(variables = infection_type_bacterial_viral_fungal_parasitic,
                  type= "level",
                  level_value = c("Fungal", "Viral")) %>%
  remove_row_type(infection_type_bacterial_viral_fungal_parasitic, type = "header") %>%
  add_stat_label(label = infection_type_bacterial_viral_fungal_parasitic ~ c("n (%)"), location = "column") %>%
  modify_column_indent(columns = label, undo = TRUE) %>% 
  bold_levels() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Infections in the first 30 days**")

@@

## Table S9. Patients with infections by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy
```{r Patients with infections by CRS, ICANS, tocilizumab use, steroid use, anakinra use and bridging therapy}
cilta %>% 
  arrange(pt_identifier, desc(any_infection)) %>% 
  distinct(pt_identifier, .keep_all = TRUE) %>% 
  select(number_prior_lines_therapy,
         number_of_prior_lines_of_therapy,
         prior_auto_sct_yes_no,
         # prior_treatment_with_any_gene_therapy_based_therapeutic_or_investigational_cellular_therapy_or_bcma_targeted_therapy_yes_no,
         Prior_bcma_therapy,
         # `Received alkylating therapy with bridging (Yes=1, No=0)`,
         # `Days from last bridging to CAR-T infusion`,
         cell_dose_million_cells,
         need_for_g_csf_post_infus_yes_1_no_0,
         cd34_stem_cell_boost_yes_1_no_0,
         need_for_ivig_yes_1_no_0,

         CRS_gradecat, ICANS_gradecat,
         delayed_neuro,
         parkinsonian_neurotoxicity_yes_no,
         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
         delayed_neuro_type,
         hlh, hlh_hlh_like_toxicities,
         steroid_use_yes_no, 
         tocilizumab_yes_no, anakinra_yes_no,
         bridging_therapy_yes_no, any_infection) %>% 
  tbl_summary(by= any_infection, 
              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
              type = list(all_dichotomous() ~ "categorical", 
                          number_of_prior_lines_of_therapy ~ "continuous")) %>%
  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Any infection**")

@@

         CRS_gradecat, ICANS_gradecat,
         delayed_neuro,
         parkinsonian_neurotoxicity_yes_no,
         other_delayed_non_parkinsonian_neurologic_toxicity_yes_no,
         delayed_neuro_type,
         hlh, hlh_hlh_like_toxicities,
         steroid_use_yes_no, 
         tocilizumab_yes_no, anakinra_yes_no,
         bridging_therapy_yes_no, any_sevinfection) %>% 
  tbl_summary(by=any_sevinfection, 
              statistic=list(all_continuous() ~ "{median} ({min}, {max})"), 
              type = list(all_dichotomous() ~ "categorical", 
                          number_of_prior_lines_of_therapy ~ "continuous")) %>%
  add_p() %>%  bold_labels() %>% add_stat_label() %>% 
  modify_header(update = all_stat_cols() ~ "**{level}**, N = {n}") %>%
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Any severe infection**")
```
